Argennon: A Scalable Cloud Based Smart Contract Platform

### 2022-07-24 tex/sections/avm.tex
Fix some whitepaper typos

An Argennon Standard Representation (ASR) is a programming language for describing argennon applications, optimized
for the architecture and properties of the Argennon platform.
Argennon supports two standard representations: One is a high level text based representation which needs
costly compilation before being executed on a hardware machine. The other is a low level binary representation which
usually can be executed, with minimal pre-processing, by a JIT compiler or an emulator. The high level
language is intended for preserving the high level information of the application logic to facilitate
platform specific compiler optimization at a host machine. The low level language, on the oder hand, is designed for
efficient direct execution of applications that are not frequently used and do not benefit from compiler optimizations.

@@

The AscEE executes the requests contained in each block of the Argennon
blockchain in a three-step procedure. The first step is the \emph{preprocessing step}. In this step, the required
data for executing requests are retrieved from the Argennon cloud, the cryptographic proofs are verified and the
helper data structures for next steps are constructed. This step is
designed in a way that can be done fully in parallel for each request without any risk of data races. The second
step is the \emph{Data Dependency Analysis (DDA) step}.
In this step by analyzing data dependency between requests, the AscEE determines requests that can be run in parallel
and requests that need to be run sequentially. This information is represented using an \emph{execution dag} data
structure and in the final step, the requests are executed using this data structure.

@@

The AscEE uses \emph{Authenticated Message Passing} for authorizing operations. In this method, every execution
session has a set of authenticated messages, and those messages are \textbf{explicitly} passed in requests to
applications for authorizing operations. These messages act exactly like digital signatures and applications can
ensure that they are issued by specific accounts. The only difference is that the process of message authentication
is performed by the AscEE internally and is not performed by the application. For accounts, the AscEE uses digital
signatures to authenticate messages. Signatures for each request can be validated in parallel during the
preprocessing step of the block validation, and any type of
cryptographic signature scheme can be used. For example, we could use BLS aggregate signature to authenticate all
messages of a block of the blockchain in bulk.

@@

The AscEE has two type of execution sessions: \emph{optimistic} and \emph{monitored}. Resource usage of an optimistic
session is always measured per session and \textbf{default} pre-defined resource caps are used. On the other hand, for a
monitored session, resources that can not be measured precisely are measured per application call and their caps are
determined per application call by the external HTTP request (i.e.\ transaction). The block proposer decides the
type of the execution session for each transaction.

>>>>

An Argennon Standard Representation (ASR) is a programming language for describing Argennon applications, optimized
for the architecture and properties of the Argennon platform.
Argennon supports two standard representations: One is a high level text based representation which needs
costly compilation before being executed on a hardware machine. The other is a low level binary representation which
usually can be executed, with minimal pre-processing, by a JIT compiler or an emulator. The high level
language is intended for preserving the high level information of the application logic to facilitate
platform specific compiler optimization at a host machine. The low level language, on the oder hand, is designed for
efficient direct execution of applications that are not frequently used and do not benefit from compiler optimizations.

@@

The AscEE executes the requests contained in each block of the Argennon
blockchain in a three-step procedure. The first step is the \emph{preprocessing step}. In this step, the required
data for executing requests are retrieved from the Argennon cloud, the cryptographic proofs are verified and the
helper data structures for next steps are constructed. This step is
designed in a way that can be done fully in parallel for each request without any risk of data races. The second
step is the \emph{Data Dependency Analysis (DDA) step}.
In this step by analyzing data dependency between requests, the AscEE determines requests that can be run in parallel
and requests that need to be run sequentially. This information is represented using an \emph{execution DAG} data
structure and in the final step, the requests are executed using this data structure.

@@

The AscEE uses \emph{Authenticated Message Passing} for authorizing operations. In this method, every execution
session has a set of authenticated messages, and those messages are \textbf{explicitly} passed in requests to
applications for authorizing operations. These messages act exactly like digital signatures and applications can
ensure that they are issued by specific accounts. The only difference is that the process of message authentication
is performed by the AscEE internally and is not performed by the application. For accounts, the AscEE uses digital
signatures to authenticate messages. Signatures for each request can be validated in parallel during the
preprocessing step of the block validation, and any type of
cryptographic signature scheme can be used. For example, we could use BLS aggregate signatures to authenticate all
messages of a block of the blockchain in bulk.

@@

The AscEE has two types of execution sessions: \emph{optimistic} and \emph{monitored}. Resource usage of an optimistic
session is always measured per session and \textbf{default} pre-defined resource caps are used. On the other hand, for a
monitored session, resources that can not be measured precisely are measured per application call and their caps are
determined per application call by the external HTTP request (i.e.\ transaction). The block proposer decides the
type of the execution session for each transaction.

### 2022-07-24 tex/sections/consensus.tex
Fix some whitepaper typos

The credibility of a block of the Argennon blockchain is determined by the certificates it has received
from different sets of users, knows as committees. There are two primary type of certificate committees in
Argennon: the committee of \emph{delegates} and the committee
of \emph{validators}. Argennon has \emph{one} committee of delegates and $m$ committees of validators.

@@

Besides the main delegates' committee, a reserve committee of delegates consists of three members is elected by users
either through the ADAGs or by \emph{emergency agreement} during the recovery protocol. In case the main committee
fails to generate new blocks or behaves maliciously, the task of
block generation will be assigned to the reserve committee until a new main delegates' committee is elected
through the ADAGs.

@@

To prevent blockchain from halting in such situations, the protocol performs a predefined partial
reshuffling of committee members.
In this reshuffling which is based on the block random seed, some online members from other committees will
be moved to the committee without enough online stake to make it active again.

If the reshuffling can not solve the problem due to low total online stake, the protocol requires the next block
of the blockchain to be a special \emph{status block}. A status block is a special block which can only contain
status change transactions. The status block need to be certified by the delegates and by 2/3 of the total stake of
validators. The \texttt{online}/\texttt{offline} status of validators will not be considered in the validity of
the status block certificate.\footnote{Theoretically at the status block, the total online stake of the system could
be very low. Therefore, the status block should not be certified only by online stake.} After applying
the transactions of the status block, the total online stake of all committees of validators
must go higher than \texttt{minOnlineStake} threshold.

@@

A validator always choose a valid fork block over a block of the main chain. However, as we mentioned before,
a validator never signs a certificate for two different blocks with the same height. Consequently, if a validator
has already signed the block $b$ of the main chain, he will not sign the fork block and vice versa.

@@

Unfortunately, there is a subtle problem with this approach. It is not clear that in a real world economic system
how much of the main currency of the system can be locked and kept out of the circulation indefinitely. It seems that
this amount for currencies like US dollar, is quite low comparing to the total market cap of the currency.
This means that for a real world currency this type of staking mechanisms will result in putting the
fate of the system in the hands of the owners of a small fraction of the total supply.

>>>>

The credibility of a block of the Argennon blockchain is determined by the certificates it has received
from different sets of users, known as committees. There are two primary type of certificate committees in
Argennon: the committee of \emph{delegates} and the committee
of \emph{validators}. Argennon has \emph{one} committee of delegates and $m$ committees of validators.

@@

Besides the main delegates' committee, a reserve committee of delegates consisting of three members is elected by users
either through the ADAGs or by \emph{emergency agreement} during the recovery protocol. In case the main committee
fails to generate new blocks or behaves maliciously, the task of
block generation will be assigned to the reserve committee until a new main delegates' committee is elected
through the ADAGs.

@@

To prevent the blockchain from halting in such situations, the protocol performs a predefined partial
reshuffling of committee members.
In this reshuffling which is based on the block random seed, some online members from other committees will
be moved to the committee without enough online stake to make it active again.

If the reshuffling can not solve the problem due to low total online stake, the protocol requires the next block
of the blockchain to be a special \emph{status block}. A status block is a special block which can only contain
status change transactions. The status block needs to be certified by the delegates and by 2/3 of the total stake of
validators. The \texttt{online}/\texttt{offline} status of validators will not be considered in the validity of
the status block certificate.\footnote{Theoretically at the status block, the total online stake of the system could
be very low. Therefore, the status block should not be certified only by online stake.} After applying
the transactions of the status block, the total online stake of all committees of validators
must go higher than \texttt{minOnlineStake} threshold.

@@

A validator always chooses a valid fork block over a block of the main chain. However, as we mentioned before,
a validator never signs a certificate for two different blocks with the same height. Consequently, if a validator
has already signed the block $b$ of the main chain, he will not sign the fork block and vice versa.

@@

Unfortunately, there is a subtle problem with this approach. It is not clear in a real world economic system
how much of the main currency of the system can be locked and kept out of the circulation indefinitely. It seems that
this amount for currencies like US dollar, is quite low comparing to the total market cap of the currency.
This means that for a real world currency this type of staking mechanism will result in putting the
fate of the system in the hands of the owners of a small fraction of the total supply.
